\documentclass[a4paper,12pt]{report}

\begin{document}

\chapter*{Acknowledgments}

Pursuing a PhD has been a long journey spanning nine years of higher studies. As I reflect on this path, I am deeply grateful for the incredible support and guidance of those around me.

First and foremost, my heartfelt gratitude goes to my parents, Neeta and Karunesh, who stood by me with unwavering support through every twist and turn. Their belief in me, even when I doubted myself, has been my greatest anchor. To my late grandmother, Kamal, whose wisdom and warmth continue to guide me, I am profoundly thankful. I also owe thanks to my sister, Mayuri, who has been my constant cheerleader since childhood. To my partner, Jasmine, thank you for being such a wonderful companion over these past three years.

I am immensely grateful to my thesis advisor, Michael, for his insightful guidance, support, and trust in me and my abilities. It was a pleasure working with you, and your mentorship has taught me invaluable lessons over these past three years.

To my colleagues in the Sign Language research group - M\&TALS and friends at LISN, thank you for fostering a collaborative and inspiring environment. Your camaraderie and insights have been a source of strength and intellectual growth.

Lastly, I deeply appreciate the Serveur Gestuel project by Bpifrance for funding my research.

To everyone who supported me, encouraged me, and believed in me, this thesis is as much yours as it is mine. Thank you for walking this path with me.

\end{document}
